Grade Retention and Mixed Race

### 2022-08-19 products/paper/main.qmd
Update biblio

First, using direct identification of biracial respondents on data sources such as the Census or large scale surveys is problematic. Research on the identification and classification of biracial individuals indicates that individuals whose parents belong to different races will not always or consistently identify with both races (==CITE==). Furthermore, social status and social mobility has been shown to predict racial identification (==CITE==) and this process of reverse causation is likely to be strongest for more ambiguous groups such as biracials. Thus, differences in outcome may in some part produce differences in identification rather than the other way around when examining biracial individuals identified by self-identification.

@@

---

>>>>

First, using direct identification of biracial respondents on data sources such as the Census or large scale surveys is problematic. Research on the identification and classification of biracial individuals indicates that individuals whose parents belong to different races will not always or consistently identify with both races [@liebler_america_2017] (==OTHER CITE?==). Furthermore, social status and social mobility has been shown to predict racial identification (==CITE==) and this process of reverse causation is likely to be strongest for more ambiguous groups such as biracials. Thus, differences in outcome may in some part produce differences in identification rather than the other way around when examining biracial individuals identified by self-identification.

@@

------------------------------------------------------------------------
